Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-26 manuscript/ERL_global_C_review.Rmd
work on discussion

All database manipulation, analyses, and figure production were fully automated in R (**version, citation**).
Materials required to fully reproduce these analyses, including data, R scripts, and image files, are archived in Zenodo (DOI: TBD].
Data, scripts, and results presented here are also available through the open-access ForC GitHub repository (https://github.com/forc-db/ForC), where many will be updated as the database develops.

@@

ForC v.XX yielded a fairly comprehensive and internally consistent picture of C cycling in the world's major forest biomes.
Carbon cycling rates generally increased from boreal to tropical regions and with stand age.
Specifically, the major C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests -- a pattern that generally held for regrowth as well as mature forests (Figs. 6-7).
In contrast to C fluxes, there was little directional variation in mature forest C stocks across biomes (Figs. 2-5, 7).
The majority of flux variables, together with most live biomass pools, increased significantly with stand age (Figs. 6-11).
Together, these results indicate that, moving from cold to tropical climates and from young to old stands, there is a general acceleration of C cycling, whereas C stocks and $NEP$ of mature forests are correlated with a different set of factors.

@@

There remain numerous data needs for improved accounting of forest carbon stocks and fluxes in GHG accounting.
AGB is the largest stock, and most of the emphasis is on this variable.
Remote sensing, with calibration based on high-quality ground-based data [@schepaschenko_forest_2019; @chave_ground_2019], is the best approach for mapping forest carbon (REFS).
However, it is limited in that it is not associated with stand age and disturbance history, except in recent decades when satellite data can be used to detect forest loss, gain, and some of their dominant drivers [@hansen_high-resolution_2013; @song_global_2018; @curtis_classifying_2018].
ForC  is therefore valuable in defining age-based trajectories in biomass, as in @cook-patton_mapping_2020.

 *remote sensing measurements are increasingly useful for global- or regional-scale estimates of forest $GPP$ (Bagdley et al. 2019, [@li_mapping_2019]), aboveground biomass ($B_{ag}$) (REFS), woody mortality (*i.e.*, $B_{ag}$ losses to mortality $M_{woody}$) [@clark_quantifying_2004; @leitold_nino_2018], and to some extent net ecosystem exchange ($NEP$) (REFS),*

Other variables, in particular respiration fluxes, cannot be remotely sensed (@bond-Lamberty_estimating_2016), and efforts such as the Global Carbon Project (**le quere REF**) and NASA CMS (**citation: https://carbon.nasa.gov/pdfs/CMS_Phase-1_Report_Final_optimized.pdf but maybe better to cite open literature, one of the papers listed at https://cmsflux.jpl.nasa.gov/get-data/publication-data-sets**) typically compute them as residuals only.

@@

>>>>

All database manipulation, analyses, and figure production were fully automated in R (**version, citation**).

@@

ForC v.XX brought together an unprecedented amount of data to yield an internally consistent picture of C cycling in the world's major forest biomes.
Carbon cycling rates generally increased from boreal to tropical regions and with stand age.
Specifically, the major C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests -- a pattern that generally held for regrowth as well as mature forests (Figs. 6-7).
In contrast to C fluxes, there was little directional variation in mature forest C stocks across biomes (Figs. 2-5, 7).
The majority of flux variables, together with most live biomass pools, increased significantly with stand age (Figs. 6-11).
Together, these results indicate that, moving from cold to tropical climates and from young to old stands, there is a general acceleration of C cycling, whereas C stocks and $NEP$ of mature forests are correlated with a different set of factors.

@@

**ForC can complement remote sensing to provide a comprehensive picture of global forest C cycling.** (*here, discuss what is well-covered by remote sesnsing, where ForC is useful for calibrating remote sensing, and what ForC can get that remote sensing can't.*)
AGB is the largest stock, and most of the emphasis is on this variable.
Remote sensing, with calibration based on high-quality ground-based data [@schepaschenko_forest_2019; @chave_ground_2019], is the best approach for mapping forest carbon (REFS).
However, it is limited in that it is not associated with stand age and disturbance history, except in recent decades when satellite data can be used to detect forest loss, gain, and some of their dominant drivers [@hansen_high-resolution_2013; @song_global_2018; @curtis_classifying_2018].
ForC  is therefore valuable in defining age-based trajectories in biomass, as in @cook-patton_mapping_2020.

*Remote sensing measurements are increasingly useful for global- or regional-scale estimates of forest $GPP$ (Bagdley et al. 2019, [@li_mapping_2019]), aboveground biomass ($B_{ag}$) (REFS), woody mortality (*i.e.*, $B_{ag}$ losses to mortality $M_{woody}$) [@clark_quantifying_2004; @leitold_nino_2018], and to some extent net ecosystem exchange ($NEP$) (REFS).*
Other variables, in particular respiration fluxes, cannot be remotely sensed (@bond-Lamberty_estimating_2016), and efforts such as the Global Carbon Project (**le quere REF**) and NASA CMS (**citation: https://carbon.nasa.gov/pdfs/CMS_Phase-1_Report_Final_optimized.pdf but maybe better to cite open literature, one of the papers listed at https://cmsflux.jpl.nasa.gov/get-data/publication-data-sets**) typically compute them as residuals only. (**Ben, it woudl be particularly helpful if you could flesh this out some more.**)

@@

## Data availability statement
Materials required to fully reproduce these analyses, including data, R scripts, and image files, are archived in Zenodo (DOI: TBD].
Data, scripts, and results presented here are also available through the open-access ForC GitHub repository (https://github.com/forc-db/ForC), where many will be updated as the database develops.

## ORCID iD
